\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{LUMP: Locking and Unlocking Mobile Platform}

### 2013-05-06 paper.tex
formalify the caption for figure 6
Edited paper

\section{Introduction}
Locks may be one of the most pervasive technologies in the world. Traditional, physical locks are used for houses, cars, windows, fences, and luggage --- every object in the world humans deem worth protecting. However, it was not always just objects themselves that were worth protecting --- it was information as well.\\

There are a few examples of this type of information security --- the first is physically protecting information by putting it in a safe with a dial \cite{safestructure}, such that turning the dial the correct amount in the correct direction a few times in sequence allows access to the contents of a box. This design allows for physical valuables to be stored in such a way that makes it only accessible to those who have knowledge of the correct sequence of physical manipulations of a lock. \\

The second type, which is more relevant in our increasingly electronic world, is the obfuscation of information through means such as ciphers, which encodes information in such a way that can only be decoded if the reader knows the algorithm, or cipher, which allows them to change the form into a human-readable format. This method is much older than the computing technology ubiquitous today, however. Classical ciphers, for example, simply substitute letters with other letters (e.g. $G$ could be always replaced with $L$). However, the problems with this sort of cipher is that it is easy to figure out an algorithm when it is simple and efficient to calculate, either by human or computer. This is the motivation behind symmetric and asymmetric encryption, which drives a great deal of authentication today. \\

@@

When transferring data over a medium which another party could potentially read, asymmetric-key encryption is preferred. Asymmetric-Key encryption is system in which users are able to share a ``public key'' insecurely with the intended recipient of some encrypted data \cite{ssl}. Additionally, a ``private key'' is generated for each of the two parties involved in the transfer such that the keys can be combined to make the data only readable to those who have the correct private and public key. This algorithm prevents anyone who has access to all data being transferred to be able to decrypt the data, because that user's private key will not be able to combine with the public key which has been distributed to allow access to the encrypted data. This type of encryption is pervasive across many types of systems, including HTTPS, which uses SSL with HTTP \cite{ssl}.  It is this implementation of asymmetric-key encryption that is relevant to this paper. \\

In the physical world, however, we cannot simply use numbers to protect our valuables. This is the reasons safes still exist and are so widely used, and is one of the motivations of this project --- to combine the convenience of software security and the protection of lockboxes. Traditionally, identity can be verified in some subset of ``what you know,'' ``what you have,'' and ``what you are.''  \cite{codinghorror} Software security implementations as described above generally rely on the ``what you know'' aspect (e.g. passwords, public and private keys, etc.) of identity verification while traditional locks rely on ``what you have'' (i.e. physical keys for a physical lock). As a result, companies  such as Google, Dropbox \cite{dropboxtwostep}, and Twitter \cite{twittertwostep} have recently begun implementing two-step verification for logging into their services. These verification processes usually rely on knowledge of a password as well as ownership of a smartphone, which provides a temporal code which can be entered into the service as a second step in the authentication process. \\

@@

iOS architecture has an architecture made up of four layers \cite{iosoverview}. The top layer is Cocoa Touch, which provides developers with standardized user interface objects such as buttons, sliders, table views, and other commonly used components \cite{cocoatouch}. Cocoa Touch also provides abstractions from lower-level functionality in a number of frameworks. Native frameworks exist for audio processing, animation and graphics development, networking, and persistent storage, among others. As its name suggests, Cocoa Touch also provides access to all touch events that occur on the device.\\

@@

One thing to note is that all networking requests are performed using the external library AFNetworking \cite{afnetworking}. AFNetworking provides a powerful wrapper around the native iOS networking classes, and makes things like basic authentication and HTTPS requests much simpler than they would be with the libraries built into iOS. AFNetworking requests allow blocks of code to be passed into network request function calls, to be executed on a successful or a failed request. This proved to be particularly useful for is, because knowing the current status of the lock at any point in time is the crux of our experiment. \\

@@

The server uses two python libraries in conjunction, \texttt{ssl} \cite{pyssl} and \texttt{BaseHTTPServer} \cite{BaseHTTPServer}, which enable a basic http server to run with an ssl socket enabled. With this, we are able to keep this server running and accepting connections, but only responding to secure requests such that the metadata sent with each request cannot be seen by third parties. \\

The server itself runs on a Raspberry Pi Model B using Python 2.7.3. The Raspberry Pi runs Raspbian \cite{raspbian}, a particular Debian distribution designed with the hardware constraints of the Raspberry Pi in mind, and comes pre-installed with Python on it. This feature combined with the simplicity of Python as a programming language made the Raspberry Pi a particularly good computer on which we could run our server. The integration of the Raspberry Pi in the hardware design of the experiment will be discussed the next section. \\

@@

\begin{figure*}[t!]
\centering
%\includegraphics[width=0.5\textwidth]{circuit.png}
\includegraphics[height=3.5in]{circuit.png}
\caption{Circuit}
\end{figure*}

The Arduino has a number of components which it controls. Pins 4 and 5 connect to a tri-color LED, which indicates whether a network connection is available or not. If not, the server cannot receive requests. Pin 4 triggers the red LED within the tri-color LED, signaling no network connection, and pin 5 triggers the blue LED within the tri-color LED, signaling successful connection to the network. Pins 6 and 7 also control a status indicating tri-color LED, which indicates whether the lock is locked or unlocked. Pin 6 triggers the red LED, and is turned on when the lock is locked, and pin 7 triggers the green LED, which is activated when the lock is unlocked. Both tri-color LEDs are connected to ground via two 100 $\Omega$ resistors. \\

@@

However, Lockitron's solution costs \$179 to pre order, and only works for doors. Our solution addresses a more general problem. Our implementation could be used on doors as well, but also on safes, lock boxes, cars, and anything else with a locking and unlocking mechanism. The simplicity of the servo implementation allows for easy, adaptable extensions for locks on nearly anything.\\

@@

\section{Future Work}
Though LUMP has most of its components working together, improvements could be made in three specific areas. The first is the mobility and adaptability of the device, the second is more physical, such that our lock ensures better physical security, and the third is better software security in terms of actual data storage.\\

With regard to mobility and adaptability, the connection between the server and the Arduino was not fully functional when the server was running on Raspberry Pi \cite{breakfastserialissue}. The connection was inconsistent and often failed for reasons we failed to completely debug. As a result, the solution relied on a more traditional laptop running a server --- an overhead that is unnecessary in both physical and fiscal cost. With the raspberry pi working, the solution would be more mobile.\\

>>>>

\section{Introduction}
Locks may be one of the most pervasive technologies in the world. Traditional, physical locks are used for houses, cars, windows, fences, and luggage --- every object in the world humans deem worth protecting. However, it is not always physical objects that are worth protecting, but information as well.\\

There are a few examples of this type of information security --- the first is physically protecting information by putting it in a safe with a dial \cite{safestructure}, such that turning the dial the correct amount in the correct direction several times in sequence allows access to the contents of a box. This design allows for physical valuables to be stored in such a way that makes it only accessible to those who have knowledge of the correct sequence of physical manipulations of a lock. \\

The second type, which is more relevant in our increasingly electronic world, is the obfuscation of information through means such as ciphers, which encode information in such a way that can only be decoded if the reader knows the algorithm, or cipher; applying the cipher to the obfuscated information allows them to change the form into a human-readable format. This method is much older than the computing technology ubiquitous today. Classical ciphers, for example, simply substitute letters with other letters (e.g. $G$ could be always replaced with $L$). However, the problems with this sort of cipher is that it is easy to figure out an algorithm when it is simple and efficient to calculate, either by human or computer. This is the motivation behind symmetric and asymmetric encryption, which drives a great deal of authentication today. \\

@@

When transferring data over a medium which another party could potentially read, asymmetric-key encryption is preferred. Asymmetric-key encryption is system in which users are able to share a ``public key'' insecurely with the intended recipient of some encrypted data \cite{ssl}. Additionally, a ``private key'' is generated for each of the two parties involved in the transfer such that the keys can be combined to make the data only readable to those who have the correct private and public key. This algorithm prevents anyone who has access to all data being transferred to be able to decrypt the data, because that user's private key will not be able to combine with the public key which has been distributed to allow access to the encrypted data. This type of encryption is pervasive across many types of systems, including HTTPS, which uses SSL with HTTP \cite{ssl}.  It is this implementation of asymmetric-key encryption that is relevant to this paper. \\

In the physical world, however, we cannot simply use numbers to protect our valuables. This is the reasons safes still exist and are so widely used, and is one of the motivations of this project --- to combine the convenience of software encryption with the physical security of lockboxes. Traditionally, identity can be verified in some subset of ``what you know,'' ``what you have,'' and ``what you are.''  \cite{codinghorror} Software security implementations as described above generally rely on the ``what you know'' aspect (e.g. passwords, public and private keys, etc.) of identity verification while traditional locks rely on ``what you have'' (i.e. physical keys for a physical lock). As a result, companies  such as Google, Dropbox \cite{dropboxtwostep}, and Twitter \cite{twittertwostep} have recently begun implementing two-step verification for logging into their services. These verification processes usually rely on knowledge of a password as well as ownership of a smartphone, which provides a temporal code which can be entered into the service as a second step in the authentication process. \\

@@

iOS architecture is made up of four layers \cite{iosoverview}. The top layer is Cocoa Touch, which provides developers with standardized user interface objects such as buttons, sliders, table views, and other commonly used user interface components \cite{cocoatouch}. Cocoa Touch also provides abstractions from lower-level functionality in a number of frameworks. Native frameworks exist for audio processing, animation and graphics development, networking, and persistent storage, among others. As its name suggests, Cocoa Touch also provides access to, and subsequent processing of, all touch events that occur on the device.\\

@@

One thing to note is that all networking requests are performed using the external library AFNetworking \cite{afnetworking}. AFNetworking provides a powerful wrapper around the native iOS networking classes, and makes things like basic authentication and HTTPS requests much simpler than they would be with the libraries built into iOS. AFNetworking requests allow blocks of code to be passed into network request function calls, to be executed on a successful or a failed request. This proved to be particularly useful for us, because knowing the current status of the lock at any point in time is the crux of our experiment. \\

@@

The server uses two python libraries in conjunction, \texttt{ssl} \cite{pyssl} and \texttt{BaseHTTPServer} \cite{BaseHTTPServer}, which enable a basic http server to run with an SSL socket enabled. With this, we are able to keep this server running and accepting connections, but only responding to secure requests such that the metadata sent with each request cannot be seen by third parties. \\

The server itself runs on a Raspberry Pi Model B using Python 2.7.3. The Raspberry Pi runs Raspbian \cite{raspbian}, a particular Debian distribution designed with the hardware constraints of the Raspberry Pi in mind; Raspbian also comes with Python pre-installed on it. This feature combined with the simplicity of Python as a programming language and the portability of the Raspberry Pi itself made the Raspberry Pi a particularly good computer on which we could run our server. The integration of the Raspberry Pi in the hardware design of the experiment will be discussed the next section. \\

@@

\begin{figure*}[t!]
\centering
%\includegraphics[width=0.5\textwidth]{circuit.png}
\includegraphics[height=3.5in]{circuit.png}
\caption{Hardware Schematic}
\end{figure*}

The Arduino has a number of components that it controls. Pins 4 and 5 connect to a tri-color LED, which indicates whether a network connection is available or not. If not, the server cannot receive requests. Pin 4 triggers the red LED within the tri-color LED, signaling no network connection, and pin 5 triggers the blue LED within the tri-color LED, signaling successful connection to the network. Pins 6 and 7 also control a status indicating tri-color LED, which indicates whether the lock is locked or unlocked. Pin 6 triggers the red LED, and is turned on when the lock is locked, and pin 7 triggers the green LED, which is activated when the lock is unlocked. Both tri-color LEDs are connected to ground via two 100 $\Omega$ resistors. \\

@@

However, Lockitron's solution costs \$179 to pre order, and only works for doors. Our solution addresses a more general problem. Our implementation could be used on doors as well, but also on safes, lock boxes, cars, and anything else with a locking and unlocking mechanism. The simplicity of the servo implementation allows for easy, adaptable extensions for locks on nearly anything. Furthermore, our implementation is significantly less expensive\\

@@

\section{Future Work}
Although LUMP has most of its components working together, improvements could be made in three specific areas. The first is the mobility and adaptability of the device, the second is more physical, such that our lock ensures better physical security, and the third is better software security in terms of actual data storage.\\

With regard to mobility and adaptability, the connection between the server and the Arduino was not fully functional when the server was running on Raspberry Pi \cite{breakfastserialissue}. The connection was inconsistent and often failed for reasons we failed to completely debug. As a result, the solution relied on a more traditional laptop running a server --- an overhead that is unnecessary in both physical and fiscal cost. With the Raspberry Pi working, the solution would be more mobile.\\
